---
title: "hw1"
author: "Rachel Ling"
date: "2/9/2022"
output: html_document
---
---
title: "Assignment 1(local)”
author: "Rachel Ling"
date: "2/1/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("knitr")
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata)

contract.service.area <- readRDS("/Users/rachelling/Downloads/contract_service_area-2.rds")
ffs.costs <-readRDS("/Users/rachelling/Downloads/ffs_costs.rds")
final.ma.data <- readRDS("/Users/rachelling/Downloads/final_ma_data.rds")
ma.benchmark <- readRDS("/Users/rachelling/Downloads/ma_benchmark.rds")
ma.penetration <- readRDS("/Users/rachelling/Downloads/ma_penetration.rds")
plan.premiums <- readRDS("/Users/rachelling/Downloads/plan_premiums.rds")
risk.rebate <- readRDS("/Users/rachelling/Downloads/risk_rebate.rds")
star.ratings <- readRDS("/Users/rachelling/Downloads/star_ratings.rds")
full.ma.data <-readRDS("/Users/rachelling/Downloads/full_ma_data.rds")
```

##Enrollment Data
# 1.How many observations are in your current dataset?
There are 19126783 observations in my dataset.
# 2. How many different plan_types are there?
```{r}

df <- full.ma.data %>% ungroup
df %>%
    filter(!is.na(plan_type)) %>%
    distinct(plan_type)
```
There are 26 different plan types. 
# 3. Provide a table of the count of plans under each plan type in each year.
```{r}
myplan_count <- full.ma.data %>%
  group_by(year, plan_type) %>%
  select(year, plan_type) %>%
  summarize(plan_count=n())

(table_planyear <- pivot_wider(myplan_count, 
                               names_from = year, 
                               values_from = plan_count))
knitr::kable(full.ma.data, col.names=c("","2007","2008","2009","2010","2011","2012","2013","2014","2015"),
             type="html", caption = "Plan Count by Year", booktabs = TRUE)
```
## 4. Remove all special needs plans (SNP), employer group plans (eghp), and all “800-series” plans.
```{r}
myplan_counts_update <- full.ma.data %>% 
  filter(snp =="No" & eghp == "No") %>%
  filter(planid <800 | planid >= 900) %>%
  filter(!is.na(planid)) %>%
  group_by(year, plan_type) %>%
  select(year, plan_type) %>%
  summarize(plan_count=n())

(table_planyear1 <- pivot_wider(myplan_counts_update, 
                               names_from = year, 
                               values_from = plan_count))
knitr::kable(full.ma.data, col.names=c("","2007","2008","2009","2010","2011","2012","2013","2014","2015"),
             type="html", caption = "Plan Count by Year", booktabs = TRUE)

```
# 5. Merge the contract service area data to the enrollment data, and restrict the data only to contracts that are approved in their respective counties.
```{r}
final.data <- full.ma.data %>%
  inner_join(contract.service.area %>% 
               select(contractid, fips, year), 
             by=c("contractid", "fips", "year")) %>%
  filter(!state %in% c("VI","PR","MP","GU","AS","") &
           snp == "No" &
           (planid < 800 | planid >= 900) &
           !is.na(planid) & !is.na(fips))
```
# 6. Finally, limit your dataset only to plans with non-missing enrollment data. Provide a graph showing the average number of Medicare Advantage enrollees per county from 2008 to 2015. 
```{r}

```

## 
## Summary Questions
#Why did we drop the "800-series" plans?
The beneficiary doesn't actually hold the contract with CMS in 800-series plans. 
#Why do so many plans charge a $0 premium? What does that really mean to a beneficiary? 
The beneficiary still has out of pocket costs they must pay such as coinsurance/copayments, deductibles, etc. 
